No need to know: astrophysics-free gravitational-wave cosmology

### 2024-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

% \new{Regardless, this systematic offset further demonstrates that incorrect parametric models induce a systematic bias in cosmological inference rather than an increased statistical uncertainty. 
% Other parametric models may show different trends depending on which parts of the mass distribution they incorrectly model and how.
% Therefore, while we are able to identify the shortcomings of \bpl{} when \plp{} describes the true mass distribution, it is not possible in practice to know which direction an incorrect parametric model will bias \Ho{}.
% Mitigating the bias by using more flexible models may thus be the simplest solution to this problem.}

>>>>

\new{Regardless, this systematic offset further demonstrates that incorrect parametric models induce a systematic bias in cosmological inference rather than an increased statistical uncertainty. 
Other parametric models may show different trends depending on which parts of the mass distribution they incorrectly model and how.
Therefore, while we are able to identify the shortcomings of \bpl{} when \plp{} describes the true mass distribution, it is not possible in practice to know which direction an incorrect parametric model will bias \Ho{}.
Mitigating the bias by using more flexible models may thus be the simplest solution to this problem.}
